Global well-being and mental health in the internet age

### 2023-05-10 ms.Rmd
Use after_stat()

x <- fits_wb %>% 
  mutate(out = map(fit, ~spread_draws(.x, `^b_.*`, regex = TRUE))) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  select(outcome, model, .draw, b_year, matches("^b_[i|m]_c[w|b]$")) %>% 
  pivot_longer(starts_with("b_"), names_to = "parameter") %>% 
  mutate(
    Predictor = case_when(
      parameter == "b_year" & model == "1" ~ "Time Within country",
      parameter == "b_i_cw" ~ "Internet Within country",
      parameter == "b_m_cw" ~ "Mobile Within country",
      parameter == "b_i_cb" ~ "Internet Between countries",
      parameter == "b_m_cb" ~ "Mobile Between countries"
    )
  ) %>% 
  drop_na(Predictor, value) %>% 
  separate(Predictor, c("Predictor", "x"), extra = "merge") %>% 
  mutate(
    Predictor = factor(
      Predictor, 
      levels = c("Time", "Internet", "Mobile")
    )
  )
p2 <- x %>%   
  ggplot(aes(value, fct_rev(Predictor), fill = x)) +
  scale_color_brewer(
    "Association", palette = "Set2", aesthetics = c("fill", "color")
  ) +
  scale_shape_manual(values = c(21, 19)) +
  scale_x_continuous(
    "Estimated linear association",
    breaks = extended_breaks()
  ) +
  stat_halfeye(
    aes(shape = stat(sign(xmax) == sign(xmin))),
    position = position_dodge(.15), 
    normalize = "xy", 
    height = .8,
    point_interval = "mean_qi",
    fatten_point = 3,
    point_fill = "white",
    size = .25,
    slab_alpha = .75,
    adjust = 1.5,
    .width = .95
    ) +
  facet_wrap(
    "outcome", 
    labeller = labeller(
      .cols = as_labeller(~str_replace(., "_", " "))
    ),
    scales = "free_x"
  ) +
  theme(
    legend.position = "none",
    axis.title.y = element_blank(),
    panel.grid.major.x = element_line(
      color = "black", linetype = "dotted", size = .1
    )
  )

@@

x <- fits_mh %>% 
  mutate(out = map(fit, ~spread_draws(.x, `^b_.*`, regex = TRUE))) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  select(outcome, model, .draw, b_year, matches("^b_[i|m]_c[w|b]$")) %>% 
  pivot_longer(starts_with("b_"), names_to = "parameter") %>% 
  mutate(
    Predictor = case_when(
      parameter == "b_year" & model == "1" ~ "Time Within country",
      parameter == "b_i_cw" ~ "Internet Within country",
      parameter == "b_m_cw" ~ "Mobile Within country",
      parameter == "b_i_cb" ~ "Internet Between countries",
      parameter == "b_m_cb" ~ "Mobile Between countries"
    )
  ) %>% 
  drop_na(Predictor, value) %>% 
  separate(Predictor, c("Predictor", "x"), extra = "merge") %>% 
  mutate(
    Predictor = factor(
      Predictor, 
      levels = c("Time", "Internet", "Mobile")
    )
  )
p2 <- x %>%   
  ggplot(aes(value, fct_rev(Predictor), fill = x)) +
  scale_color_brewer(
    "Association", palette = "Set2", aesthetics = c("fill", "color")
  ) +
  scale_shape_manual(values = c(21, 19)) +
  scale_x_continuous(
    "Estimated linear association",
    breaks = extended_breaks(),
    # From percentages in model to rates per 100k
    labels = ~ . * 1000,
  ) +
  stat_halfeye(
    aes(shape = stat(sign(xmax) == sign(xmin))),
    position = position_dodge(.15), 
    normalize = "xy", 
    height = .8,
    point_interval = "mean_qi",
    fatten_point = 3,
    point_fill = "white",
    size = .25,
    slab_alpha = .75,
    adjust = 1.5,
    .width = .95
    ) +
  facet_wrap(
    "outcome", 
    labeller = labeller(
      .cols = as_labeller(~str_replace(., "_", " "))
    ),
    scales = "free_x"
  ) +
  theme(
    legend.position = "none",
    axis.title.y = element_blank(),
    panel.grid.major.x = element_line(
      color = "black", linetype = "dotted", size = .1
    )
  )

>>>>

x <- fits_wb %>% 
  mutate(out = map(fit, ~spread_draws(.x, `^b_.*`, regex = TRUE))) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  select(outcome, model, .draw, b_year, matches("^b_[i|m]_c[w|b]$")) %>% 
  pivot_longer(starts_with("b_"), names_to = "parameter") %>% 
  mutate(
    Predictor = case_when(
      parameter == "b_year" & model == "1" ~ "Time Within country",
      parameter == "b_i_cw" ~ "Internet Within country",
      parameter == "b_m_cw" ~ "Mobile Within country",
      parameter == "b_i_cb" ~ "Internet Between countries",
      parameter == "b_m_cb" ~ "Mobile Between countries"
    )
  ) %>% 
  drop_na(Predictor, value) %>% 
  separate(Predictor, c("Predictor", "x"), extra = "merge") %>% 
  mutate(
    Predictor = factor(
      Predictor, 
      levels = c("Time", "Internet", "Mobile")
    )
  )
p2 <- x %>%   
  ggplot(aes(value, fct_rev(Predictor), fill = x)) +
  scale_color_brewer(
    "Association", palette = "Set2", aesthetics = c("fill", "color")
  ) +
  scale_shape_manual(values = c(21, 19)) +
  scale_x_continuous(
    "Estimated linear association",
    breaks = extended_breaks()
  ) +
  stat_halfeye(
    aes(shape = after_stat(sign(xmax) == sign(xmin))),
    position = position_dodge(.15), 
    normalize = "xy", 
    height = .8,
    point_interval = "mean_qi",
    fatten_point = 3,
    point_fill = "white",
    size = .25,
    slab_alpha = .75,
    adjust = 1.5,
    .width = .95
    ) +
  facet_wrap(
    "outcome", 
    labeller = labeller(
      .cols = as_labeller(~str_replace(., "_", " "))
    ),
    scales = "free_x"
  ) +
  theme(
    legend.position = "none",
    axis.title.y = element_blank(),
    panel.grid.major.x = element_line(
      color = "black", linetype = "dotted", size = .1
    )
  )

@@

x <- fits_mh %>% 
  mutate(out = map(fit, ~spread_draws(.x, `^b_.*`, regex = TRUE))) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  select(outcome, model, .draw, b_year, matches("^b_[i|m]_c[w|b]$")) %>% 
  pivot_longer(starts_with("b_"), names_to = "parameter") %>% 
  mutate(
    Predictor = case_when(
      parameter == "b_year" & model == "1" ~ "Time Within country",
      parameter == "b_i_cw" ~ "Internet Within country",
      parameter == "b_m_cw" ~ "Mobile Within country",
      parameter == "b_i_cb" ~ "Internet Between countries",
      parameter == "b_m_cb" ~ "Mobile Between countries"
    )
  ) %>% 
  drop_na(Predictor, value) %>% 
  separate(Predictor, c("Predictor", "x"), extra = "merge") %>% 
  mutate(
    Predictor = factor(
      Predictor, 
      levels = c("Time", "Internet", "Mobile")
    )
  )
p2 <- x %>%   
  ggplot(aes(value, fct_rev(Predictor), fill = x)) +
  scale_color_brewer(
    "Association", palette = "Set2", aesthetics = c("fill", "color")
  ) +
  scale_shape_manual(values = c(21, 19)) +
  scale_x_continuous(
    "Estimated linear association",
    breaks = extended_breaks(),
    # From percentages in model to rates per 100k
    labels = ~ . * 1000,
  ) +
  stat_halfeye(
    aes(shape = after_stat(sign(xmax) == sign(xmin))),
    position = position_dodge(.15), 
    normalize = "xy", 
    height = .8,
    point_interval = "mean_qi",
    fatten_point = 3,
    point_fill = "white",
    size = .25,
    slab_alpha = .75,
    adjust = 1.5,
    .width = .95
    ) +
  facet_wrap(
    "outcome", 
    labeller = labeller(
      .cols = as_labeller(~str_replace(., "_", " "))
    ),
    scales = "free_x"
  ) +
  theme(
    legend.position = "none",
    axis.title.y = element_blank(),
    panel.grid.major.x = element_line(
      color = "black", linetype = "dotted", size = .1
    )
  )
